---
title: "Welcome!"
subtitle: "<br>Talk 1: Text analysis in R: Special Christmas Edition<br><br>Talk 2: Interactive Dashboards with shiny"
output:
  xaringan::moon_reader:
    css: ["default", "shinobi", "ninjutsu", "cards.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

class: center, inverse

# LA and OC R User Groups
<br>
#[https://laocr.org](https://laocr.org)
<br>
## LA East and West R Users/DSLA
## R-Ladies Los Angeles
## R-Ladies Pasadena
## R-Ladies Irvine
## Orange County R Users Group

---

class: inverse

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(htmltools)
library(here)

events <- read_rds(here("events.rds"))
past_events <- read_rds(here("past_events.rds"))

clean_events <- function(events_data, descending = FALSE) {
  months <- lubridate::month(events_data$time)
  month_abbs <- month.abb[months]
  days <- lubridate::day(events_data$time)
  hours <- format(strptime(events_data$local_time, "%H:%M"), "%I:%M %p")
  events_data$event_time <- paste(month_abbs, days, "at", hours)
  
  if (descending) {
    events_data <- arrange(events_data, desc(time))
    } else {
    events_data <- arrange(events_data, time)
  }
  
  events_data %>% 
    select(event_name = name, group_name, event_time, link)
}

as_card <- function(event_name, group_name, event_time, link, ...) {
  tags$div(
    class = "card",
    tags$a(href = link,
      class = "action_link",
      div(class = "container",
        tags$div(group_name, class = "card-group"),
        tags$div(event_name, class = "card-header"),
        tags$div(event_time, class = "card-time")
      )
    )
  )
}
```

```{r, echo=FALSE}
cards <- clean_events(events) %>% 
  filter(group_name != "Los Angeles East R Users Group") %>% 
  pmap(as_card)
```

`r tagList(cards)`

---
class: center, inverse

# Next Month

<br>

## Time Series & ARIMA forecasting
## TBD

--
<br><br><br>
### Let us know if you want to give a talk!
---

class: center, inverse

# February: 

<br>

## `rstudio::conf() %>% debrief()`

---

class: center, inverse

# March: 

<br>

## `lightning_talks(time = "5min")`

---

class: center, middle, inverse

<br>

## Thanks to the Department of Preventive Medicine at USC for supporting and feeding us!
# 🍕🍕🍕

---

class: center, middle, inverse

# Keep in touch! 
<br>

### `r icon::fa("slack")` [bit.ly/laerug](http://bit.ly/laerug)
### `r icon::fa("twitter")` [@laeRusers](https://twitter.com/laeRusers)
### `r icon::fa("github")` [laeRusers](https://github.com/laeRusers/)
### `r icon::fa("envelope")` [laerug@gmail.com](mailto:laerug@gmail.com)
### `r icon::fa("globe")` [laocr.org](https://lacor.org)

<br>
Slides created via the R package [xaringan](https://github.com/yihui/xaringan).