---
title: "Welcome!"
subtitle: "<br>Talk 1: Getting better at R By Learning More Packages More Deeply<br><br>Talk 2: This time it's personal: Livecoding a personal R pkg"
output:
  xaringan::moon_reader:
    css: ["default", "shinobi", "ninjutsu", "cards.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

class: center, inverse

# SoCal R User Groups
<br>
#[https://socalr.org](https://socalr.org)
<br>
### LA East and West R Users/DSLA
### R-Ladies Los Angeles
### R-Ladies Pasadena
### R-Ladies Irvine
### Orange County R Users Group
### Santa Barbara R Users Group
### R-Ladies Santa Barbara 
### R-Ladies San Diego
### San Diego R Users Group
### San Luis Obispo R Users Group

---

class: inverse

```{r, echo=FALSE, message=FALSE}
source(here::here("R", "packages.R"))
source(here::here("R", "functions.R"))

events <- read_rds(here::here("data", "events.rds"))
past_events <- read_rds(here::here("data", "past_events.rds"))
```

```{r, echo=FALSE}
cards <- clean_events(events) %>% 
  filter(group_name != "Los Angeles East R Users") %>% 
  pmap(as_card)
```

`r tagList(cards)`

---

class: center, middle, inverse

# Next Month

<br>

## Teaching R
## Spatial Analysis in R

--

<br><br><br>
### Let us know if you want to give a talk!

---

class: center, middle, inverse

<br>

## Thanks to the Department of Preventive Medicine at USC for supporting and feeding us!
# 🍕🍕🍕

---

class: center, middle, inverse

# Keep in touch! 
<br>

### `r icon::fa("slack")` [https://socalrug.herokuapp.com/](https://socalrug.herokuapp.com/)
### `r icon::fa("twitter")` [@la_Rusers](https://twitter.com/la_Rusers)
### `r icon::fa("github")` [laRusers](https://github.com/laRusers/)
### `r icon::fa("envelope")` [larusers@gmail.com](mailto:larusers@gmail.com)
### `r icon::fa("globe")` [socalr.org](https://socalr.org)

<br>
Slides created via the R package [xaringan](https://github.com/yihui/xaringan).
