---
title: "Southern California R Users Group"
page-layout: full
toc: false
---

```{r}
#| include: false

source(here::here("helpers", "class_cards.R"))
events <- readRDS(file.path("events", "events_past_and_upcoming.rds"))
```

Welcome to the Southern California R Users Group (SoCal RUG)! Since no single group can serve this sprawling area, several RUGs from Santa Barbara to San Diego joined forces to centralize SoCal-based R events and information.

In addition to our core SoCal RUG team, our archive includes events hosted by our extended R alliance including the following groups: [R-Ladies Irvine](https://www.rladiesirvine.org/), [R-Ladies Los Angeles](https://www.meetup.com/rladies-la/), [R-Ladies Pasadena](https://www.meetup.com/rladies-pasadena/), [R-Ladies Riverside](https://rladies.github.io/riverside/), [R-Ladies Santa Barbara](https://www.meetup.com/rladies-santa-barbara/), [R-Ladies San Diego](https://www.meetup.com/rladies-san-diego/), [Santa Barbara RUG](https://www.meetup.com/Santa-Barbara-R-Users-Group/), and [San Luis Obispo RUG](https://www.meetup.com/useR-Group-in-San-Luis-Obispo-County/).

***

::: {.callout-tip}
## Upcoming Events
:::

```{r}
#| echo: false

upcoming_events <- events |> dplyr::filter(Upcoming != "")

if (nrow(upcoming_events) == 0) {
  paste("Stay Tuned! There are no scheduled upcoming events.")
} else {
  htmltools::tagList(
    upcoming_events |> 
      purrr::pmap(as_card_upcoming)
  )
}
```

***

::: {.callout-note}
## Past Events
:::

```{r}
#| echo: false

htmltools::tagList(
  events |> 
    dplyr::filter(Upcoming == "") |> 
    purrr::pmap(as_card)
)
```
