---
title: "Southern California R Users Group"
page-layout: full
toc: false
---

```{r}
#| include: false

events <- readRDS("events/events_past_and_upcoming.rds")
```

Welcome to the Southern California R Users Group (SoCal RUG)! Since no single group can serve this sprawling area, several Los Angeles and Orange County groups joined forces to centralize SoCal-based R events and information.

In addition to our core SoCal RUG team, our archive includes events hosted by our extended R alliance including the following groups: [R-Ladies Irvine](https://www.rladiesirvine.org/), [R-Ladies Los Angeles](https://www.meetup.com/rladies-la/), [R-Ladies Pasadena](https://www.meetup.com/rladies-pasadena/), [R-Ladies Riverside](https://rladies.github.io/riverside/), [R-Ladies Santa Barbara](https://www.meetup.com/rladies-santa-barbara/), [R-Ladies San Diego](https://www.meetup.com/rladies-san-diego/), [Santa Barbara RUG](https://www.meetup.com/Santa-Barbara-R-Users-Group/), [San Luis Obispo RUG](https://www.meetup.com/useR-Group-in-San-Luis-Obispo-County/), and [San Diego RUG](https://www.meetup.com/sd-r-users/).

# Events Archive

```{r}
#| echo: false

library(kableExtra)

events |> 
  knitr::kable(align = c("c", "l", "l", "l", "l"), escape = FALSE) |> 
  kableExtra::kable_styling(bootstrap_options = "basic") |> 
  kableExtra::column_spec(column = 2, width = "15em") |> 
  kableExtra::column_spec(column = 4, width = "7em") |> 
  kableExtra::column_spec(column = 5, width = "6em")
```
